
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in, top=0.4in, right=0.4in, bottom=0.4in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Gaddam Bhanu Venkata Abhiram} 

\address{
\href{tel:+919398982703}{+91 9398982703} \\ 
\href{mailto:gaddamabhiram53@gmail.com}{gaddamabhiram53@gmail.com} \\ 
\href{https://www.linkedin.com/in/abhiramgaddam/}{linkedin.com/in/abhiramgaddam}
}

\begin{document}

%-------------------
% EDUCATION
%-------------------
\begin{rSection}{Education}
\textbf{Bachelor of Computer Science and Business Systems} \hfill 2022 -- 2026 (Expected) \\
R.V.R \& J.C College of Engineering, Guntur \hfill CGPA: 8.65/10
\end{rSection}

%-------------------
% SKILLS
%-------------------
\begin{rSection}{Skills}
\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l}
Languages/Frameworks & Java, JavaScript, React.js, Node.js, Express.js \\
Web Technologies & HTML5, CSS3, Tailwind CSS, RESTful APIs \\
Databases & MongoDB, MySQL \\
Cloud \& Tools &  Git, GitHub, Postman, Vercel \\
Design Principles & Software Design, Object-Oriented Programming (OOP)
\end{tabular}
\end{rSection}

%-------------------
% INTERNSHIPS
%-------------------
\begin{rSection}{Internships}
\textbf{Technical Associate - 4Sight AI (Andhra Pradesh Police)} \hfill May 2025 -- Jun 2025
\begin{itemize}
    \item Developed responsive web applications using React.js for large-scale event management, serving 400+ high-profile dignitaries.
    \item Engineered a QR-based verification system to optimize the authentication process for invitations and certificates.
    \item Collaborated with technical teams to solve real-time software engineering problems during a state-level hackathon.
\end{itemize}
\end{rSection}

%-------------------
% PROJECTS
%-------------------
\begin{rSection}{Projects}

\textbf{Webinar \& Certification Platform (Global Academy of Embryology)} 
\begin{itemize}
    \item Developed a full-stack application for a real-world client, managing 500+ active users.  
    
    \item Integrated AWS S3 for secure asset storage and MongoDB for scalable data management of faculty and user profiles.
    \item Built a QR-code authentication feature allowing external parties to verify certificate validity via the platform.
    \item Developed comprehensive Dashboards for Admins to perform CRUD operations on webinars and faculty data.
\end{itemize}

\textbf{Restaurant Management System (MERN Stack)} 
\begin{itemize}
    \item Engineered a full-stack system with role-based access control, optimizing table booking and order workflows.
    \item Developed RESTful APIs supporting end-to-end workflows from menu browsing to dynamic billing and order handling.
    \item Applied software design principles to create reusable UI components, reducing frontend development time by 20\%.
\end{itemize}

\textbf{Movie Recommendation Engine} 
\begin{itemize}
    \item Built a content-based recommendation system using TF-IDF and Cosine Similarity on a dataset of 5,000+ titles.
    \item Integrated OMDb API for real-time metadata retrieval, applying scientific methods to improve recommendation relevance.
\end{itemize}

\end{rSection}

%-------------------
% CERTIFICATIONS
%-------------------
\begin{rSection}{Certifications}
\begin{itemize}
    \item \textbf{Java Object-Oriented Programming} – LinkedIn Learning
    \item \textbf{React Js Specialization} – Infosys Springboard
    \item \textbf{The Complete MySQL Bootcamp} – Udemy
\end{itemize}
\end{rSection}

\end{document}